How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-11 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

There were 28,008 downloaded studies, and 9,632 (34\%) had a statistical methods section.

@@

>>>>

There were 28,008 downloaded studies, and 9,632 (34\%) had a statistical methods section.
Of the 12,700 eligible applications, 9523 (75%) had a statistic section

Variable & Odds ratio & 95% CI
Study type = Observational & 0.78 & 0.69, 0.89
Date (per year) & 0.90 & 0.88, 0.91
Number of funders & 0.80 & 0.74, 0.86
Target sample size (per doubling) & 0.90 & 0.88, 0.92

@@

One reason these inadequate sections get published is that most journals do not use statistical reviewers, despite empirical evidence showing they improve manuscript quality [@Hardwicke2020].
